---
title: Developing Data Products Course Week 4 Assignment
author: "M. Liu"
date: "July 11, 2018"
output:
  #ioslides_presentation: default (obsolete)
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Brief Introduction

 - This presentation is the week 4 assignment of Coursera Couurse ***Developing Data Products course from Coursera*** (<https://www.coursera.org/learn/data-products>). 
 
 - This presentation was generated using ***RStudio***(<https://www.rstudio.com>) and ***Slidify***(<http://slidify.org>) framework.

## Application Development

 - An instance of the web application is up and running at https://mliu5408.shinyapps.io/MPGPrediction.
 
 - This shows a web application using R and [Shiny](https://shiny.rstudio.com) framework together.
 
 - A prediction model is developed using a car parameters dataset (HP, weight, gears, etc.). A web application user can play with the UI values to simulate the parameters of an hypothetical car to predict its MPG consumption.
 
 - All files of this assignment are stored at https://github.com/mliu5408/data-products-week-4-project. To view the files, we need to copy and paste the url to a brower. This is a secuirity repirement.    

   The web application comprises 3 files: *ui.R* (UI), *server.R* (backend) and *modelBuilding.R* (Random Forest predictor) under the folder ***source***. 

   The R Markdown code of this presentation is named data-products-week-4-project.Rmd. 

   The presentation is published on http://rpubs.com/mliu5408/403756. 

   A README.md file in Markdown format is also stored in the same github location.
  
## Training Dataset

Dataset used for training and model building is the [Motor Trend Car Road Tests](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) (or *'mtcars'*). The data was extracted from the ***1974 Motor Trend*** US magazine, comprising fuel consumption and 10 aspects of automobile design as well as performance features for 32 automobiles (1973-74 models).

The dataset structure is as follows: 
```{r cars, echo = TRUE}
str(mtcars)
```

## Fuel Consumption Prediction

A Random Forest predictive model is built and trained using the *'mtcars'* dataset to predict the fuel consumption (***mpg***) based on the features of the automibiles.

```{r echo = FALSE}
suppressWarnings(suppressMessages(library(caret)))
suppressWarnings(suppressMessages(library(randomForest)))

set.seed(290195)

```

```{r echo = TRUE}
customTrainControl <- trainControl(method = "cv", number = 10)
carsRandomForestModelBuilder <- function() {
  return(
    train(
      mpg ~ ., 
      data = mtcars,
      method = "rf",
      trControl = customTrainControl
    )
  )
}

carsRandomForestModelBuilder()
```
